---
title: "Practice drawing vector maps"
output: html_document
---

```{r packages}
library(tidyverse)
library(sf)
library(colorspace) # for better color palettes
library(here)       # for specifying directory location

theme_set(theme_minimal())  # could choose something better for maps
```

## Import information on median household income in 2017 for Cook County, IL at the tract-level using the ACS

```{r}
cook_county_path <- here("data", "cook-county-inc.geojson")
cook_inc <- st_read(______ = cook_county_path)
cook_inc
```

## Draw a choropleth using the median household income data

- Use a continuous color gradient to identify each tract's median household income

```{r}
# use fill channel
ggplot(data = _____) +
  geom_sf(mapping = aes(fill = _____)) +
  scale_fill_*_*()

# use fill and color channels - what is the difference?
...
```

## Draw the same choropleth for Cook County, but convert median household income into a discrete variable with 6 levels

- Using `cut_interval()`

```{r}
cook_inc %>%
  ______(______ = ______) %>%
  ggplot() +
  geom_sf(mapping = aes(fill = inc_cut, color = inc_cut))
```
        
- Using `cut_number()`

```{r}
cook_inc %>%
  ______(______ = ______) %>%
  ggplot() +
  geom_sf(mapping = aes(fill = inc_cut, color = inc_cut))
```

- Using `binned_scale()`

```{r}
# default breaks
ggplot(data = cook_inc) +
  geom_sf(mapping = aes(fill = estimate, color = estimate)) +
  scale_fill_*_*(aesthetics = c("fill", "color"), ...)

# quartiles
ggplot(data = cook_inc) +
  geom_sf(mapping = aes(fill = estimate, color = estimate)) +
  scale_fill_*_*(aesthetics = c("fill", "color"), ...)
```

## Draw a choropleth of median household income for each US county

- Adjust to use Albers equal-area projection

```{r}
usa_inc <- st_read(dsn = here("data", "usa-inc.geojson"))
usa_inc
```

```{r}
ggplot(data = ______) +
  geom_sf(mapping = aes(fill = ______, color = ______)) +
  ______(______ = ______)
```

## Session Info

```{r}
sessioninfo::session_info()
```
